\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-24 WOOT/Files/introduction.tex
Update intro

The rest of this paper is structured as follows:
\shuqing{Fill in after the structure is finalized.}

>>>>

The rest of this paper is structured as follows.
Section~\ref{sec:background} provides the background of USB specification.
Section~\ref{sec:related_work} introduces the existing work of USB security from the aspects of attacking and defence respectively.
In Section~\ref{sec:badusb}, we present the threat model and the overall implementation of \tool in three different modes.
The experiments and user study we conducted are featured in Section~\ref{sec:experiment}.
We presents the possible countermeasures of \tool in Section~\ref{sec:countermeasures}.
The limits and impacts of our approach are discussed in Section~\ref{sec:discussion}, and the conclusion lies in Section~\ref{sec:conclusion}.
%\shuqing{Fill in after the structure is finalized.}
